Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article.tex
Add red horizontal lines for confidence interval in figure 2a

  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc1.png}
    \label{fig:hydrophobicity_1}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc2.png}
    \label{fig:hydrophobicity_2}
  \end{subfigure}  
  \caption{ \textbf{Over-presentation of TMH-derived epitopes on most MHC-I and -II haplotypes}
    \textbf{(A)} 
    The percentage of epitopes for MHC-I and -II haplotypes that are predicted to 
    overlap with TMHs for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (MtB; bottom row).
    The pair of dashed lines in each plot indicate the lower and upper bound of the 99\% confidence interval.
    See supplementary Tables \ref{tab:tmh_binders_mhc2} and \ref{tab:tmh_binders_mhc1}
    for the exact TMH and  epitope counts.
    \textbf{(B-C)}
    Correlation between the percentages of predicted TMH-derived epitopes
    and the hydrophobicity score of all predicted epitopes for MHC-I \textbf{(B)}
    and MHC-II haplotypes \textbf{(C)}. \textbf{GEERT: are panels B-C done with human, SARS-CoV-2 or MtB?}
    Diagonal red line: linear regression analysis. 
    Labels are shorthand for the HLA haplotypes,
    see the supplementary Table \ref{tab:haplotype_abbreviations} for the names.
  }
\end{figure}

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented.
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. \textbf{GEER: zie comment in main text: wellicht rode horizontale streep bij verwachtingswaarde, net als in Fig 1A? Maakt manuscript veel duidelijker}
  }
  \label{fig:elution}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2c.png}
  \caption{
    \textbf{
      TMH-derived epitopes are over-presented when using
      predicted as well as experimental data
    }
    For the MHC class I alleles, the over-presentation of
    TMH-derived epitopes is correlated between 
    IEDB MHC ligand epitopes (horizontal axis) and the 9-mers
    derived from a human reference proteome (vertical axis).
    The trendline shows the linear correlation between these
    percentages, where the gray area is the 95\% confidence interval.
  }
  \label{fig:thm_presentation_correlation}
\end{figure}

>>>>

  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc1.png}
    \label{fig:hydrophobicity_1}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc2.png}
    \label{fig:hydrophobicity_2}
  \end{subfigure}  
  \caption{ \textbf{Over-presentation of TMH-derived epitopes on most MHC-I and -II haplotypes}
    \textbf{(A)} 
    The percentage of epitopes for MHC-I and -II haplotypes that are predicted to 
    overlap with TMHs for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (MtB; bottom row).
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval.
    See supplementary Tables \ref{tab:tmh_binders_mhc2} and \ref{tab:tmh_binders_mhc1}
    for the exact TMH and  epitope counts.
    \textbf{(B-C)}
    Correlation between the percentages of predicted TMH-derived epitopes
    and the hydrophobicity score of all predicted epitopes for MHC-I \textbf{(B)}
    and MHC-II haplotypes \textbf{(C)}. \textbf{GEERT: are panels B-C done with human, SARS-CoV-2 or MtB?}
    Diagonal red line: linear regression analysis. 
    Labels are shorthand for the HLA haplotypes,
    see the supplementary Table \ref{tab:haplotype_abbreviations} for the names.
  }
\end{figure}

@@

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles
    that overlap with TMHs that are presented.
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    MHC ligands from IEDB binding to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay. \textbf{GEER: zie comment in main text: wellicht rode horizontale streep bij verwachtingswaarde, net als in Fig 1A? Maakt manuscript veel duidelijker}
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval.
  }
  \label{fig:elution}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2c.png}
  \caption{
    \textbf{
      TMH-derived epitopes are over-presented when using
      predicted as well as experimental data
    }
    For the MHC class I alleles, the over-presentation of
    TMH-derived epitopes is correlated between 
    IEDB MHC ligand epitopes (horizontal axis) and the 9-mers
    derived from a human reference proteome (vertical axis).
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    The trendline shows the linear correlation between these
    percentages, where the gray area is the 95\% confidence interval.
  }
  \label{fig:thm_presentation_correlation}
\end{figure}
